Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-08 PreregristrationS3/PreregistrationAOT-M.Rmd
introduction adjusted

In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998]. A key condition for these contact benefits, has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015]. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b]. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met. It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.

>>>>

In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998]. A key condition for these contact benefits has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015]. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b]. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met [@Pettigrew2006]. It, thus, remains unclear why and how exactly Allport's conditions work.
